A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-10-14 sections/introduction/main.tex
Include more references of news reports

There are various news reports that indicate that this is in fact an ongoing 
issue that affects both the patients and the ambulance service.
Emergency departments (EDs) are constantly under a lot of pressure to meet 
targets and satisfy regulations \cite{EmergencyDepartmentWinterPressures}.
These additional targets imply that the ED staff must also be able to manage 
the flow of patients.
% TODO: Reference papers/news reports + Wider search of news reports -> BMJ

>>>>

Emergency departments (EDs) are constantly under a lot of pressure to meet 
targets and satisfy regulations \cite{EmergencyDepartmentWinterPressures}.
There are various news reports that indicate that this is in fact an ongoing 
issue that affects both the patients and the ambulance service.
Due to this blockage patients may spend a considerable amount of time in the 
back of an ambulance waiting to be dispatched to the ED \cite{mirror}, 
\cite{thenews}, \cite{bmj}.
On the other hand though this can also cause ambulances to waste valuable time 
where they could be attending to new patients \cite{eastanglia}.
